Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-05 paper/paper.tex
fix typo in introduction

Behind the overarching challenge of coming up with a robust predictive challenge for human behavior, the main practical application of timbre similarity retrieval lies in the emerging topic of computer-assisted instrumentation \cite{maresz2013cmr}.
Following the aesthetic tradition of spectralism in contemporary music creation, the composer queries the machine with an arbitrary audio signal.
The outcome of this is an instrumental audio sample, alongside textual attributes of playing technique.
In this context, the computer serves as a bridge from the auditory level to the symbolic level, allowing to approximate a potentially infinite realm of timbral sensations by an orchestra of priorly specified extent and technical range.
To maximize the perceptual fidelity of such an approximation, a query-by-example search engine in the auditory domain should summarize the vastest possible vocabulary of timbral templates.

>>>>

Behind the overarching challenge of coming up with a robust predictive model for human behavior, the main practical application of timbre similarity retrieval lies in the emerging topic of computer-assisted instrumentation \cite{maresz2013cmr}.
Following the aesthetic tradition of spectralism in contemporary music creation, the composer queries the machine with an arbitrary audio signal.
The outcome of this is an instrumental audio sample, alongside textual attributes of playing technique.
In this context, the computer serves as a bridge from the auditory level to the symbolic level, allowing to approximate a potentially infinite realm of timbral sensations by an orchestra of priorly specified extent and technical range.
To maximize the perceptual fidelity of such an approximation, a query-by-example search engine in the auditory domain should summarize the vastest possible vocabulary of timbral templates.
